Psychological Needs During Intergroup Contact

### 2021-11-04 Methods-and-Results.Rmd
tbl spacing fix attempt

workerMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/workerVarDescr.tex")
```

@@

workerOutMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/workerOutVarDescr.tex")

@@

studentMlCor %>%
  kable(
    .,
    caption = "Student: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/studentVarDescr.tex")
```

@@

studentOutMlCor %>%
  kable(
    .,
    caption = "Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/studentOutVarDescr.tex")

@@

```{r medicalVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

medicalMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/medicalVarDescr.tex")
```

```{r medicalOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

medicalOutMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kableExtra::landscape() %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/medicalOutVarDescr.tex")

>>>>

workerMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/workerVarDescr.tex")
```

@@

workerOutMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/workerOutVarDescr.tex")

@@

studentMlCor %>%
  kable(
    .,
    caption = "Student: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/studentVarDescr.tex")
```

@@

studentOutMlCor %>%
  kable(
    .,
    caption = "Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/studentOutVarDescr.tex")

@@

```{r medicalVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

medicalMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/medicalVarDescr.tex")
```

```{r medicalOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

medicalOutMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  landscape() %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/medicalOutVarDescr.tex")
